Propositions as Sessions, Mechanically

### 2015-04-28 paper/presentation.tex
Finished slides (minus some revision).

\begin{frame}[fragile]
\ftitle{Translation from GV to CP : Work in Progress}{1}
\begin{theorem}[Translation]
If a GV term is well-typed then its translation is well-typed in CP.
\end{theorem}
Issues
\begin{itemize}
\item type inference, positive cases and duplication
\end{itemize}
\begin{coqp}
trans_case:
  forall L $S_1$ $S_2$ M NL NR P QL QR G H z
         (INFM: inferTy M G ($S_1$ $\with$ $S_2$))
         (TR: transTm M G 0 P)
         (TRNL: forall x (NIN: x $\notin$ L),
                  transTm (open NL x) (x $\sim$ $S_1$ ++ H) z QL)
         (TRNR: forall x (NIN: x $\notin$ L),
                  transTm (open NR x) (x $\sim$ $S_2$ ++ H) z QR),
  transTm (tm_case M NL NR) (G++H) z
          ($\nu \sem{S_1 \with S_2}$t.(P $\mid$ 0 CASE QL OR QR))
\end{coqp}
\note{

continuation-passing style.

A well-typed term in GV is parameterised by a name representing the channel
which communicates the result of its translation

@@

\begin{frame}
\frametitle{Issues and Guidelines}
\begin{itemize}
\item representation
\item modularisation
\item automation
\item reuse
\end{itemize}
\note{
  representation, modularisation(?), automation, reuse
}
\end{frame}

@@

\begin{frame}
\oldframetitle{Future Work}
\begin{itemize}
\item difficulties in formalisation
\item implications
\item future work
\end{itemize}
\note{

>>>>

\begin{frame}[fragile]
\ftitle{Translation from GV to CP : Work in Progress}{1}
\begin{theorem}[Translation]
If a GV term is well-typed then its translation is well-typed in CP:
If $\Phi \tpgv~M\of{T}$ then
$\sem{M}x \tpcp~\dualbt{\sem{\Phi}},x\of{\sem{T}}$
\end{theorem}
Issues
\begin{itemize}
\item type inference, positive cases and duplication
\end{itemize}
\begin{coqp}
trans_case:
  forall L $S_1$ $S_2$ M NL NR P QL QR G H z
         (INFM: inferTy M G ($S_1$ $\with$ $S_2$))
         (TR: transTm M G 0 P)
         (TRNL: forall x (NIN: x $\notin$ L),
                  transTm (open NL x) (x $\sim$ $S_1$ ++ H) z QL)
         (TRNR: forall x (NIN: x $\notin$ L),
                  transTm (open NR x) (x $\sim$ $S_2$ ++ H) z QR),
  transTm (tm_case M NL NR) (G++H) z
          ($\nu \sem{S_1 \with S_2}$t.(P $\mid$ 0 CASE QL OR QR))
\end{coqp}
\note{

A well-typed term in GV is parameterised by a name representing the channel
which communicates the result of its translation\\~\\

due to locally nameless translation requires type inference procedure to
obtain binders for corresponding CP process. environment may not have variable
(impossible, only well-typed terms are translated) \\~\\

solution: instead of defining functionally, use inductive type to specify only
positive cases

problem: requires much of the details from the CP/GV definitions such as
linear environment splitting and cofinite quantification (for both CP and GV!)
even if GV term with no binders e.g. function application.

@@

\begin{frame}
\frametitle{Issues and Guidelines}
\begin{itemize}
\item Representation
\item Modularisation
\item Automation
\item Reuse
\end{itemize}
\note{

  representation is a central issue when formalising languages and choices
  impact future definitions and properties dependent on them. Considerations
  range from how much expressive power provided by the theorem prover to
  exploit to the choice of which encoding to use for the properties of
  interest. Some decisions may impact upon the correspondence between the
  formal and informal systems.

  Modularising the development was essential to reduce the interactive load
  time and mitigate crashes.

  Automation advise use of non-trivial tactics favour proof search over
  in-place macros for oft-repeated sequences. It is worth considering
  situations where automation would simplify proofs. Automation is already an
  important consideration in the interactive theorem proving
  community. Examples of automation from the current development have been
  highlighted, but particular emphasis should be placed on tactics involving
  non-trivial proof search of the context because these tend to be more widely
  applicable.

  Reuse libraries wherever possible: programming language assistance but also
  helpful tactics not present in standard Coq (added some to solve permutation
  goals)

@@

\begin{frame}
\ftitle{Future Work}{3}
\begin{itemize}
\item Further investigate top-level cut elimination
\item Make progress on translation
\item Support polymorphism and $n$-ary branch and choice
\item Alternate forms of alias control (adoption and focus)
\end{itemize}
\note{

  resolve issues with proving top-level cut elimination either by constructing
  explicit derivations or by defining a suitable induction on the current
  definition. however, for the latter approach it is unclear how to obtain the
  desired relationship between subprocesses of cut

  Further progress on the current inductive definition of the translation can
  be made and then limiting the extent of duplication would be another aim

  the development currently does not support polymorphism and has only binary
  branch and choice. extending the system to support these features would
  bring it in line with extensions of the original cp/gv system.

  lastly, investigating alternate forms of alias control such as the adoption
  and focus system which allows controlled aliasing of linear objects may be
  worth formal study in the context of session types.
